---
format: 
  revealjs:
    logo: "image/logo.png"
    slide-number: c
---

#  {background-image="image/logo.png" background-size="50%"}

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = F,
                      fig.align = "center",
                      fig.retina = 3,
                      warning = F,
                      message = F)
```

```{r packages}
library(tidyverse)
library(gghighlight)
library(gganimate)
library(packcircles)
#library(viridis)
```

## Nalanda Academy {style="color: green"}

::: callout-note
## Note

These slides are work in progress.
:::

## Nalanda Academy

::: panel-tabset
## Nalanda Academy

This is the parent organisation.

## Digital Nalanda

This is an on-line platform of Nalanda Academy.
:::

# Student Mapping

```{r import-data}

student_raw <- read_csv("data/student_raw.csv")

#glimpse(student_raw)

# remove columns
student <- student_raw |>
  select(-c(Timestamp, name, aadhaar,
            mobile, email, address,
            "upload 10th class certificate/mark-sheet"))

student <- student |> 
  mutate(across(where(is.character),as_factor))

#str(student)
```

## Number of Students

```{r student-numbers}
student |> 
  mutate(year = as_factor(year)) |> 
  group_by(year) |> 
  summarise(n = n()) |>
  drop_na() |> 
  ggplot(aes(year, n)) +
  geom_col(fill = "#e5f6ff") +
  geom_line()+                            # line plot
  geom_line(size = 1, color="#1192e8", group = 1) +
  geom_point(shape=21, color="#1192e8", fill="#002d9c", size=4) +
  theme_minimal(base_size = 12) +
 
  labs(
    x = "Year",
    y = "Number of Students"
  ) +
geom_text(aes(label = n),
          vjust = 0.9,hjust=-0.5,
          fontface = "bold",
          color = "black")  

```

```{r student-type-plot}
#| eval: false

#Student Type
student |> 
  drop_na(student_type) |> 
  mutate(student_type = fct_infreq(student_type)) |> 
  group_by(student_type) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(student_type),
             fill = student_type)) +
  geom_col(width = 0.5) +
  gghighlight(max(n),
              max_highlight = 2L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Type",
    caption = "The total number of student is 877"
  )
```

## Age

```{r age-plot-old}
#| eval: false
student |> 
  drop_na(age) |> 
  mutate(age = fct_infreq(age)) |> 
  group_by(age) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(age),
             fill = age)) +
  geom_col(width = 0.5) +
  gghighlight(max(n),
              max_highlight = 2L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Age Group",
    caption = "The total number of student is 877"
  ) 
```

```{r age-plot}
# Generate the layout
data<-student |> 
  drop_na(age) |> 
  mutate(age = fct_infreq(age)) |> 
  group_by(age) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100)
packing <- circleProgressiveLayout(data$perc, sizetype='area')
packing$radius <- 0.95*packing$radius
data <- cbind(data, packing)
dat.gg <- circleLayoutVertices(packing, npoints=50)

# Plot 
ggplot() + 
  geom_polygon(data = dat.gg, aes(x, y, group = id, fill=id), colour = "black", alpha = 0.9) +
  scale_fill_viridis()+
  scale_fill_distiller(palette = "Blues") +
  geom_text(data = data, aes(x, y, size=perc, label =sprintf("%s (%s%%) \n %s", n, round(perc,0),fct_rev(age)) ), color="black") +
  theme_minimal(base_size = 0) +
  theme(legend.position="none")+ 
  labs(
    x = "Count",
    y = "Age Group",
    caption = "The total number of student is 877"
  ) +
  coord_equal()
  
  

```

## Gender

```{r gender-plot}

student |> 
  drop_na(gender) |> 
  mutate(gender = fct_infreq(gender)) |> 
  group_by(gender) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(gender),
             fill = gender)) +
  geom_col(width = 0.5) +
  gghighlight(max(n),
              max_highlight = 2L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Gender",
    caption = "The total number of student is 877"
  )
```

```{r caste-plot}
#| eval: false
student |> 
  drop_na(category) |> 
  mutate(category = fct_infreq(category)) |> 
  group_by(category) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(category),
             fill = category)) +
  geom_col() +
  gghighlight(max(n),
              max_highlight = 2L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Caste Category",
    caption = "The total number of student is 877"
  ) 
```

```{r religion-plot}
#| eval: false
student |> 
  drop_na(religion) |> 
  mutate(religion = fct_infreq(religion)) |> 
  group_by(religion) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(religion),
             fill = religion)) +
  geom_col(width = 0.5) +
  gghighlight(max(n),
              max_highlight = 2L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Religion Group",
    caption = "The total number of student is 877"
  )
```

## Medium of School Education

```{r edu-medium-plot}
student |> 
  drop_na(edu_medium) |> 
  mutate(edu_medium = fct_infreq(edu_medium)) |> 
  group_by(edu_medium) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(edu_medium),
             fill = edu_medium)) +
  geom_col(width = 0.5) +
  gghighlight(max(n),
              max_highlight = 3L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "School Medium",
    caption = "The total number of student is 877"
  )
```

## Discipline of Education

```{r stream-plot}
student |> 
  drop_na(stream) |> 
  mutate(stream = fct_infreq(stream)) |> 
  group_by(stream) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(stream),
             fill = stream)) +
  geom_col(width = 0.5) +
  gghighlight(max(n),
              max_highlight = 2L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Discipline of Education",
    caption = "The total number of student is 877"
  )
```

## Education

```{r education-plot}
student |> 
  drop_na(education) |> 
  mutate(education = fct_infreq(education)) |> 
  group_by(education) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(education),
             fill = education)) +
  geom_col(width = 0.5) +
  gghighlight(max(n),
              max_highlight = 2L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Level of Education",
    caption = "The total number of student is 877"
  )
```

## Place

```{r state-plot}
student |> 
  drop_na(state) |> 
  mutate(state= fct_infreq(fct_lump_n(state, n=3))) |> 
  group_by(state) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(state),
             fill = state)) +
  geom_col(width = 0.5) +
  gghighlight(max(n),
              max_highlight = 2L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "State of India",
    caption = "The total number of student is 877"
  )
```

## Fathers' Education

```{r father-edu-plot}
student |> 
  drop_na(father_edu) |> 
  mutate(father_edu = fct_infreq(father_edu)) |> 
  group_by(father_edu) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(father_edu),
             fill = father_edu)) +
  geom_col(width = 0.5) +
  gghighlight(max(n),
              max_highlight = 3L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Level of Education",
    caption = "The total number of student is 877"
  )
```

## Mothers' Education

```{r mother-edu-plot}
student |> 
  drop_na(mother_edu) |> 
  mutate(mother_edu = fct_infreq(mother_edu)) |> 
  group_by(mother_edu) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(mother_edu),
             fill = mother_edu)) +
  geom_col(width = 0.5) +
  gghighlight(max(n),
              max_highlight = 2L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Level of Education",
    caption = "The total number of student is 877"
  )
```

## Annual Family Income

```{r income-plot}
student |> 
  drop_na(income) |> 
  mutate(income = fct_infreq(income)) |> 
  group_by(income) |> 
  summarise(n = n()) |> 
  mutate(perc = n/sum(n)*100) |> 
  ggplot(aes(x = n,
             y = fct_rev(income),
             fill = income)) +
  geom_col(width = 0.5) +
  scale_y_discrete(labels = function(y) 
    stringr::str_wrap(y, width = 15)) +
  gghighlight(max(n),
              max_highlight = 1L) +
  geom_text(aes(label = sprintf("%s (%s%%)", n, round(perc,0))),
            hjust = 1.1,
            fontface = "bold",
            color = "black"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none") +
  labs(
    x = "Count",
    y = "Group of Income",
    caption = "The total number of student is 877"
  )
```

## Nalanda Academy Team

::: panel-tabset
## Director

Anoop Kumar

## Co-Founders

Sapna

Kapil

## Heads

-   Manisha

-   Deepak

-   Minakshi

-   Nilesh

-   Ajay

## Educators

-   Sachin

-   Rahul

-   Pranali
:::

## Nalanda Abhiyan Campus
